### 2025-02-15 paper/sections/other/constraints.qmd
very interesting

    # Counterfactuals:
    target = 2
    factual = 1
    if !any(isnothing.(x))
        yhat = [argmax(y) for y in eachcol(model(x))]
        yhat0 = [argmax(y) for y in eachcol(model(x0))]
        idx_plotted = yhat.==target .&& yhat0.==factual
        if any(idx_plotted)

>>>>

    # Counterfactuals:
    target = 2
    factual = 1
    if !any(isnothing.(x))
        yhat = [argmax(y) for y in eachcol(model(x))]
        yhat0 = [argmax(y) for y in eachcol(model(x0))]
        idx_plotted = yhat0.==factual
        if any(idx_plotted)
